# When to boostrap
1. distribution of statistic is unknown
    - Boostrapping is non-parametric, so it has no distibutional assumptions
2. when the sample is too small for inference
    - boostrapping is resampling with replacement
3. expand on a pilot study
    - estimate the population variance by creating the distribution
    - can be used for power calculations to inform a larger study
4. estimating error of the statistic is not feasible
    - the standard error of the statistic of the boostrapped samples
    - i.e. r-squared
## Risks
When the underlying distribution is unknown, and lacks a finite variance (i.e. heavy tailed, power law) then the boostrap's distribution will not follow similar convergence.
```{r, eval = FALSE}
install.packages("boot")
```

Testing it out on some data
```{r}
library(boot)
coin <- sample(0:1, 10, replace = TRUE)
b_mean <- function(x, i) mean(x[i], trim = 0)
coin_mean <- boot(coin,
    statistic = b_mean, R = 100)
plot(coin_mean)
boot.ci(coin_mean)
```
